A continuous urbanization index to assess phylogenetic adaptations in urban bird living

### 2018-05-03 ms.Rmd
Adding some structure to the results section.

Despite the number of studies which have investigated the relationships between species' traits and urban adaptedness, most studies are either spatially limited, such as a single city or region [@blair1996land; @kark2007living; @croci2008does]; or temporally limited to a single breeding season [@blair1996land] or even two month survey period [@kark2007living]]. Fortunately, citizen science [see reviews by @devictor2010beyond; @tulloch2013realising; @bonney2014next; @kobori2016citizen] can provide broad-scale empirical datasets, allowing us to test hypotheses at spatial and temporal scales previously difficult to attain. This data provides a cost-effective method to research the relationship between species' traits and urban observations. Indeed, various projects have used citizen science data to elucidate information on abundance and distribution of birds in urban ecosystems [@mccaffrey2005using; @callaghan2017assessing], as well as functional composition of urban birds [@la2014role; @morelli2016evidence; @lepczyk2017global]. However, we unaware of any projects which use citizen science observations to assess species' traits in relation to urban environments over a large spatial and temporal scale.

@@

## Bird observation data
We collated observations from eBird [@sullivan2009ebird; @sullivan2014ebird], a large-scale empirical dataset contributed by citizen scientists. Volunteer birdwatchers submit lists of species seen or heard at a given location, over a user-determined duration and survey area [@wood2011ebird]. We downloaded the eBird basic dataset (version ebd_relFeb-2018; available here: https://ebird.org/data/download), and used all observations between January 1, 2010 - February 28, 2018. This time-frame was used because this is the period in which eBird data are richest and because this time period minimized undue leverage of mismatch between changes in the response variable measurement (see response variable below) over the given time frame in which bird observations were collected.

@@

Only species which had complete data for the list of candidate traits were considered in the analyses, and we thereby ended with 549 species which met this criteria.

@@

```{r Figure 1, echo=FALSE, fig.cap="An example of five different species' average radiance values"}
knitr::include_graphics("final figures for paper/Figure1.pdf")
```

```{r Figure 2, echo=FALSE, fig.cap="The distribution, on a log-scale, of the response variable for the 569 species included in the analysis, with five example species highlighted."}
knitr::include_graphics("final figures for paper/Figure2.pdf")
```

```{r Figure 3, echo=FALSE, fig.cap="A phylogenetic tree of the birds yata yata yata...."}
knitr::include_graphics("final figures for paper/Figure3.pdf")
```

@@

>>>>

Despite the number of studies which have investigated the relationships between species' traits and urban adaptedness, most studies are either spatially limited, such as a single city or region [@blair1996land; @kark2007living; @croci2008does]; or temporally limited to a single breeding season [@blair1996land] or even two month survey period [@kark2007living]]. Fortunately, citizen science [see reviews by @devictor2010beyond; @tulloch2013realising; @bonney2014next; @kobori2016citizen] can provide broad-scale empirical datasets, allowing us to test hypotheses at spatial and temporal scales previously difficult to attain. This data provides a cost-effective method to research the relationship between species' traits and urban observations. Indeed, various projects have used citizen science data to elucidate information on abundance and distribution of birds in urban ecosystems [@mccaffrey2005using; @callaghan2017assessing], as well as functional composition of urban birds [@la2014role; @morelli2016evidence; @lepczyk2017global]. However, we are unaware of any projects which use citizen science observations to assess species' traits in relation to urban environments over a large spatial and temporal scale.

@@

## Bird observation data
We collated observations from eBird [@sullivan2009ebird; @sullivan2014ebird], a large-scale empirical dataset contributed by citizen scientists. Volunteer birdwatchers submit lists of species seen or heard at a given location, over a user-determined duration and survey area [@wood2011ebird]. We downloaded the eBird basic dataset (version ebd_relFeb-2018; available here: https://ebird.org/data/download), and used all observations between January 1, 2010 - February 28, 2018. This time-frame was used because this is the period in which eBird data are richest and because this time period minimized undue leverage of mismatch between changes in the response variable measurement (see below) over the given time frame in which bird observations were collected.

@@

Only species which had complete data for the list of candidate traits were considered in the analyses, and we thereby ended with 477 species which met this criteria.

@@

```{r Figure 1, echo=FALSE, fig.cap="An example of five different species' average radiance values."}
knitr::include_graphics("final figures for paper/Figure1.pdf")
```

```{r Figure 2, echo=FALSE, fig.cap="The distribution, on a log-scale, of the response variable for the 477 species included in the analysis, with five example species highlighted."}
knitr::include_graphics("final figures for paper/Figure2.pdf")
```

```{r Figure 3, echo=FALSE, fig.cap="A phylogenetic tree of the birds with the tips colored based on the urbanization index. The urbanization index is also shown based on the size of the bar associated with a species."}
knitr::include_graphics("final figures for paper/Figure3.pdf")
```

```{r Figure 4, echo=FALSE, fig.cap="Parameter estimates for each of the four modelling approaches employed in the analysis. A star represents a significant effect. Note that the model-averaged results do not contain every possible predictor variable in the case that a given predictor variable was not included in the top model set."}
knitr::include_graphics("final figures for paper/Figure4.pdf")
```

```{r Figure 5, echo=FALSE, fig.cap="Proportional differences for parameter estimates from the non-phylogenetically constrained and phylogenetically constrained models."}
knitr::include_graphics("final figures for paper/Figure5.pdf")
```

@@

```{r Figure S2, echo=FALSE, fig.cap="Phylogenetic uncertainty for some of the most important predictor variables included in the analysis."}
knitr::include_graphics("figures/accounting_for_phylo_uncertainty.pdf")
```
